---
title: "joss dot cat"
bibliography: citations.bibtex
format: html
css: style_changes.css
toc: true
toc-location: left
toc-title: "Contents:"
linkcolor: "#885e22"
mainfont: FiraGo
monofont: Fira Code
reference-location: margin
cap-location: margin
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache = FALSE,
                      autodep = TRUE)
library(knitr)        # file conversion
library(tidyverse)    # data manipulation
library(kableExtra)   # make tables
```

![A drawing of a domestic short-haired tabby housecat with stripes all over its body. The housecat is sitting and licking its right paw. It was drawn by Takashi Mifune and [used with permission](https://www.irasutoya.com/p/terms.html).](cat_irasutoya.png)

## What?

Hello! Welcome to joss dot cat, a small website dedicated to cat facts that I enjoy thinking about. I also have links and references to other places to learn about cats. I'm still learning and there's a lot I don't know. I welcome comments and criticism.


## Why?

Cats are the best and coolest animals currently alive today.^["Cat" refers to any animal in the Felidae family.] I like thinking about them and looking at them and maybe you do, too.


## Cat Facts

### Housecat Facts

Facts about _Felis catus_, the common housecat and the animal that most people thing of when they see the word "cat".

- Housecats have very efficient livers. This is cuz they evolved from a species of desert wildcat, which also had efficient livers and don't need to drink water very often [@Bradshaw_2013].

<!-- ### Amur Tiger Facts

Facts about a group of animals within _Panthera tigris altaica_. Amur tigers are highly endangered. -->

### Cat Pokémon Facts

Here are all the Pokémon described as cats or sufficiently cat-like in the Pokémon video game series.

:::{.column-page-inset-right}
```{r}
# read the csv file + then display it

pkmn_list <- read.csv("pokemon_list.csv") |>
  kbl() |>
  kable_styling()
pkmn_list
```
:::

Some more facts:

- There are a total of 25 cat Pokémon as of Generation VIII.
- Generation IV and VII are tied for largest number of cat Pokémon per generation---5 each.
- Generation VIII has one 1 cat Pokémon, and is therefore the worst generation.
- Strangely, my favorite Pokémon isn't a cat. Of those that are cats, it's a difficult decision between Skitty, Litten, and Zeraora. 


## Cat Resources

### Science

- The [Cat Specialist Group](http://www.catsg.org/) is a collective of cat specialists who work with endangered cats.

### Art

- [catcrumb](https://catcrumb.tumblr.com/) is an archive of cats drawn daily. Most of the drawings were done in MS Paint. I like them.
- add the tiger a day blog :>


## Contact

Feel free to email me at `czdzw3c6@duck.com` if:

- You spotted an error on this website.
- You have a cat fact to share and a source to verify that fact.
- You are a cat researcher and wanna share preprints or data.
- You took a pic of a cat and want me to see.
- You had a dream about being eaten by a lion and need to let someone know.
- Literally anything about any member of the Felidae family.

Thanks for visiting! Have a great day! :D
